A Transdiciplinary approach to developing a spectral numerical coastal-flow

### 2019-08-27 literature_review.Rmd
literature review script updated. tested out refs. word file output updated

---
title: 'A Transdiciplinary approach to developing a spectral numerical coastal-flow
  model based on passive macroalgal rafting phenenomea to shed light on ambient and
  stochastic dispersal and connectivity of nearshore and offshore marine communities
  hydrodynamic modelling in and around the coast of South Africa: Combining ecology and 3D hyperspectral'
author: "Ross Coppin"
output:
  word_document:
    fig_caption: yes
    toc: yes
---

@@

# Summary

Marine ecosystems are maintained by a variety of complex interactions between abiotic and biotic variables such as temperature, wave exposure, pH, competition, and processes such as top-down and bottom-up control, predator-prey relationships and phenology (Doney et al. 2011; Harley et al. 2006; Burrows et al. 2011; McGowan et al. 1998). These abiotic and biotic variables, the interactions between them, and the various ecological processes, ultimately determine the community composition and ecological functioning of all ecosystems (Guimaraes & Coutinho 1996; Harley et al. 2006; Poloczanska et al. 2013; Jennings & Brander 2010; Polovina 2005; Johnson et al. 2011; Wernberg et al. 2016; Dayton et al. 1999). Climate directly and indirectly affects the way in which abiotic and biotic variables interact, but is often compounded by other impacts such as habitat destruction, pollution, and overfishing (Blamey et al. 2012; Blamey et al. 2015). Temperature and wave exposure have been recognised as important variables with regards to climate-driven changes within the ocean (Guimaraes & Coutinho 1996; McGowan et al. 1998; McQuaid & Branch 1984; Laufkötter et al. 2015; Belkin 2009; Filbee-Dexter et al. 2018; Miller et al. 2011; Smale et al. 2011; Smale & Moore 2017). In order to persist and survive within variable and changing environments, organisms must either migrate, adapt, or die.

>>>>

---
title: 'A Transdiciplinary approach to developing a spectral numerical coastal-flow
  model based on passive macroalgal rafting phenenomea to shed light on ambient and
  stochastic dispersal and connectivity of nearshore and offshore marine communities
  hydrodynamic modelling in and around the coast of South Africa: Combining ecology and 3D hyperspectral'
author: "Ross Coppin"
output:
  word_document:
    fig_caption: yes
    toc: yes
bibliography: refs.bib
---

@@

# Summary
@Bolton2010
Marine ecosystems are maintained by a variety of complex interactions between abiotic and biotic variables such as temperature, wave exposure, pH, competition, and processes such as top-down and bottom-up control, predator-prey relationships and phenology (Doney et al. 2011; Harley et al. 2006; Burrows et al. 2011; McGowan et al. 1998). These abiotic and biotic variables, the interactions between them, and the various ecological processes, ultimately determine the community composition and ecological functioning of all ecosystems (Guimaraes & Coutinho 1996; Harley et al. 2006; Poloczanska et al. 2013; Jennings & Brander 2010; Polovina 2005; Johnson et al. 2011; Wernberg et al. 2016; Dayton et al. 1999). Climate directly and indirectly affects the way in which abiotic and biotic variables interact, but is often compounded by other impacts such as habitat destruction, pollution, and overfishing (Blamey et al. 2012; Blamey et al. 2015). Temperature and wave exposure have been recognised as important variables with regards to climate-driven changes within the ocean (Guimaraes & Coutinho 1996; McGowan et al. 1998; McQuaid & Branch 1984; Laufkötter et al. 2015; Belkin 2009; Filbee-Dexter et al. 2018; Miller et al. 2011; Smale et al. 2011; Smale & Moore 2017). In order to persist and survive within variable and changing environments, organisms must either migrate, adapt, or die.
